Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-18 paper.tex
Split SATCHMO and KBS related work; rewrite SATCHMO

\paragraph{Mixed-Mode Reasoning.}
Some knowledge-based reasoning systems, e.g.\ Algernon (TODO ref) and EYE (TODO ref), support combined forward and backward (\enquote*{mixed-mode}) reasoning.
However, to our knowledge, rules in these systems cannot change the assumptions available to forward rules, so they do not require incrementality.
Nevertheless, our technique bears some resemblance to the RETE algorithm (TODO ref) for forward reasoning in large knowledge bases.

The Prolog-based first-order theorem prover SATCHMO (TODO ref) and its many descendants also use mixed-mode reasoning.
SATCHMO's search procedure can be viewed as a special case of our technique: a given set of implications are used as forward rules and a single non-forward rule performs case analysis on disjunctive hypotheses.
A SATCHMO-style prover may benefit from our incremental approach if the set of implications is large, though in a setting where unification is cheap it is not clear whether avoiding repeated unifications outweighs the cost of maintaining the forward state.
SATCHMO also employs an optimisation that \enquote*{focuses} forward reasoning on the hypothesis established by the last case split, which provides a form of incrementality.

>>>>

\paragraph{SATCHMO.}
The SATCHMO first-order theorem prover (TODO ref) uses a search procedure that treats a given set of implications as forward rules and uses a single non-forward rule to perform case analysis on disjunctive hypotheses.
SATCHMO-style provers may benefit from our incremental approach if the set of implications is large.
However, since unification is comparatively cheap in first-order logic, it is not clear whether avoiding repeated unifications outweighs the cost of maintaining the forward state.
SATCHMO also employs an optimisation that \enquote*{focuses} forward reasoning on the hypothesis established by the last case split, providing a different form of incrementality.

\paragraph{Knowledge-Based Systems.}
Some knowledge-based reasoning systems, e.g.\ Algernon (TODO ref) and EYE (TODO ref), support combined forward and backward reasoning.
However, to our knowledge, no such system allows non-forward rules to change the assumptions available to forward rules, so they do not require incrementality.
Nevertheless, our technique bears some resemblance to the RETE algorithm (TODO ref) for forward reasoning in large knowledge bases.
